Comparative analysis of PMV Models accuracy implemented in the ISO 7730:2005 and ASHRAE 55:2023

### 2024-10-04 Manuscript/src/sections/introduction.tex
feat(introduction): added limitations and inaccuracies of the pmv-ce

\subsection{\ac{pmv-ce} Limitations}\label{subsec:pmv-ce-limitations}
The rationale for using the \ac{pmv-ce} model is that the original \ac{pmv} formulation cannot accurately estimate latent and sensible heat losses from the skin to the environment when \ac{v}~$>$~\qty{0.1}{\m\per\s}.
However, this method has some limitations.
Firstly, it should be noted that over the years, the critical value of \ac{v} has been changed, from \qty{0.15}{\m\per\s} in \mycite{Schiavon2014} to \qty{0.2}{\m\per\s} in the ASHRAE 55--2017~\cite{ASHRAE552017, arens_moving_2009} to \qty{0.1}{\m\per\s} in \gls{55}~\cite{ashrae552023}.
Secondly, calculating the \ac{pmv-ce} is more computationally intensive and complex since it requires the user to solve two heat balance equations, the \ac{pmv} and the \ac{set}.
Thirdly, we could not find any peer-reviewed scientific publication that quantified the accuracy improvements of this model over the original \ac{pmv}.
Finally, the \ac{set} temperature which is used to calculate the \ac{ce}, is defined as the hypothetical isothermal environment at a \ac{rh} of \qty{50}{\percent}, \ac{v}~$\leq$~\qty{0.1}{\m\per\s}, and \ac{tr}~=~\ac{tdb} in which the total heat loss from the skin of an imaginary occupant wearing clothing, standardized for the activity concerned, is the same as that from a person in the actual environment with actual clothing and activity level~\cite{ashrae552023}.
However, while \ac{v}, used to calculate the \ac{pmv-ce}, is set to \qty{0.1}{\m\per\s} the value of \ac{rh} and \ac{clo} are not adjusted to compensate for the fact that \ac{set} fixed the \ac{rh} to \qty{50}{\percent} and standardized the clothing to the activity.
We could not find a rationale for this choice in the available literature.

>>>>

\subsection{\ac{pmv-ce} Limitations}\label{subsec:pmv-ce-limitations}
The rationale for using the \ac{pmv-ce} model is that the original \ac{pmv} formulation cannot accurately estimate latent and sensible heat losses from the skin to the environment when \ac{v}~$>$~\qty{0.1}{\m\per\s}~\cite{huang_applicability_2014}.
\mycite{huang_applicability_2014} showed the \ac{set} model is more accurate than the \ac{pmv} model in predicting thermal sensation votes when subjects are exposed to air movement that are not uniformly distributed across the body.
However, they never compared the accuracy of the \ac{pmv-ce} with the \ac{pmv} model.
Using the \ac{set} model to change the inputs in the \ac{pmv} model has several limitations and inaccuracies listed below.
However, we could not find a rationale for the assumptions used to calculate the \ac{pmv-ce} in the available literature.
\begin{enumerate}
    \item Despite the fact that the \ac{ce} is used to partially estimate the heat losses from the skin to the environment, the \ac{pmv-ce} model is still using the underlying equations of the \ac{pmv} model.
    Hence, if \mycite{huang_applicability_2014} claim that the \ac{pmv} model is inaccurate when the skin has begun to sweat, then the \ac{pmv-ce} model would be equally inaccurate to the \ac{pmv} when the following inputs are passed to the model: \ac{tdb}~=~\ac{tr}~=~\qty{29}{\celsius}, \ac{rh}~=~\qty{80}{\percent}, \ac{v}~=~\qty{0.15}{\m\per\s}, \ac{met}~=~\qty{1.4}{met}, \ac{clo}~=~\qty{0.5}{clo}.
    This hypothetical person would be sweating and the \ac{pmv-ce} would only account for the small increase in cooling effect due to the air movement of \qty{0.15}{\m\per\s}, however, it would still not properly account for the evaporative heat loss caused by the hot and humid environment.
    \item It should be noted that over the years, the critical value of \ac{v} has been changed, from \qty{0.15}{\m\per\s} in \mycite{Schiavon2014} to \qty{0.2}{\m\per\s} in the ASHRAE 55--2017~\cite{ASHRAE552017, arens_moving_2009} to \qty{0.1}{\m\per\s} in \gls{55}~\cite{ashrae552023}.
    \item Calculating the \ac{pmv-ce} is more computationally intensive and complex since it requires the user to solve two heat balance equations, the \ac{pmv} and the \ac{set} model.
    \item We could not find any peer-reviewed scientific publication that quantified the accuracy improvements of this model over the original \ac{pmv} model.
    \item The \ac{set} temperature which is used to calculate the \ac{ce}, is defined as the hypothetical isothermal environment at a \ac{rh} of \qty{50}{\percent}, \ac{v}~$\leq$~\qty{0.1}{\m\per\s}, and \ac{tr}~=~\ac{tdb} in which the total heat loss from the skin of an imaginary occupant wearing clothing, standardized for the activity concerned, is the same as that from a person in the actual environment with actual clothing and activity level~\cite{ashrae552023}.
    However, while \ac{v}, used to calculate the \ac{pmv-ce}, is set to \qty{0.1}{\m\per\s} the value of \ac{rh} and \ac{clo} are not adjusted to compensate for the fact that \ac{set} fixed the \ac{rh} to \qty{50}{\percent} and standardized the clothing to the activity.
    \item The \ac{pmv-ce} assumption of keeping \ac{rh} constant after adjusting \ac{tdb} and \ac{tr} is incorrect since the value of \ac{rh} is a function of the \ac{tdb}.
    The \ac{rh} should be re-calculated, potentially assuming the humidity ratio to be constant, to reflect the new \ac{tdb} value.
\end{enumerate}
